\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-15 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
making corrections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Introduction}\label{section:Intro}
\medskip
Numerical investigation and modelling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years. Characterization of the flow of fluids through porous media serves as the foundation of reservoir engineering studies. Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations. Out of this mixed and complex formations, viscous flow instabilities can occur both within a single phase or when multiple phases flow through porous media. Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account. Injections of low-viscosity, high-density fluid $1$ (e.g. water) into a reservoir saturated with lighter but more viscous oil is an example where both viscous and gravitational instabilities may occur for two-phase immiscible and incompressible flow. These phenomena have great importance during the oil and gas recovery operations in both mature and new fields. Starting from oil and gas migration of contaminants through groundwater is the opposite problem governed by the same principles. The most complicated of processes include fingering that wil loccur in multiphase and compositional flow. Underground coal gasification is another potential application but more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Introduction}\label{section:Intro}
\medskip
Numerical investigation and modelling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years. Characterization of the flow of fluids through porous media serves as the foundation of reservoir engineering studies. Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations. Oil and gas migration, transport of contaminants through groundwater are some of important physical problem that porous media flows play a crucial role. Underground coal gasification, for the mining industry is an important area of interest, but more recently, also due to the global environmental problems, research focus on the CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilization and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.

\medskip
Out of this mixed and complex various geological formations, multiphase flows through porous media. play the most important role in understanding the afformentioned operations. These often involves the displacement of a non-wetting invading fluid from a porous medium by a wetting fluid. Modeling of multiphase flow, on the other hand is still an enormous technical and computational challenge. In all branches of fluid mechanics, there are the instabilities, also know as flow instabilities. The first distinction should be made between microscopic and macroscopic instabilities. The term microscopic instabilities is used for the phenomena occurring locally; for example, the Helmholtz and Taylor instabilities or bubble collapse. On the other hand the macroscopic instabilities involve, e.g.the entire two-phase flow system. In this paper, the main focus is kept on macroscopic phenomena. Part of flow instabilities is the viscous flow instabilities also know as \textit{viscous fingering}. In large scale field operations it is the condition whereby the interface of two fluids, such as oil and water, bypasses sections of reservoir as it moves along, creating an uneven, or fingered, profile. Fingering is a relatively common condition in reservoirs with water-injection wells. The result of fingering is an inefficient sweeping action that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores. It can occur both within a single phase or when multiple phases flow through porous media.

%Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account. Injections of low-viscosity, high-density fluid (e.g. water) into a reservoir saturated with lighter but more viscous oil is an example where both viscous and gravitational instabilities may occur for two-phase immiscible and incompressible flow. These phenomena have great importance during the oil and gas recovery operations in both mature and new fields.
